The Bot on Speaking Terms: The Effects of Conversation Architecture on Perceptions of Conversational Agents

### 2023-02-22 sections/4-findings.tex
Young-Ho edit and fix citations/references

The category of \textbf{dialog strategy} refers to the approach used by a conversational agent to engage in a dialogue with a user, which includes the use of social dialogs, agent-initiated content, and adding delays to responses. Specifically, the element of \textit{social dialogue} captures non-task related conversations with the user to build social connection, such as self-disclosure \cite{lee2020hear}\cmt{[23]} and small talk like chitchats \cite{lubold2016effects}\cmt{[86]}\cite{volkel2021manipulating}\cmt{[68]}. The element of \textit{initiative} captures utterances that are initiated by the agent without direct prompts from the user. For example, the agent is taking the initiative to proactively repair the conversation with a user \cite{ashktorab2019resilient}\cmt{[88]}\cite{cuadra2021my}\cmt{[67]}, or actively elicit feedback from users \cite{xiao2021let}\cmt{[73]}. Lastly, \textit{response delay} refers to the tactic of deliberatively delaying for a certain period of time before an agent responds to users \cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2022opposing}\cmt{[20]}. It is mainly used in text-based CAs alongside visual displays of typing indicators \cite{gnewuch2018chatbot}\cmt{[21]}.

\textbf{Content affectiveness} refers to the conversational agent's use of language to convey emotions or to elicit emotions from users. The architecture element of \textit{affective language} captures the injection of emotional words or phrases into the agent's utterance, such as affective expressions \cite{seeger2021chatbots}\cmt{[35]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}, sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, and encouraging words \cite{healey2013relating}\cmt{[39]}. The other element in this category, \textit{humour}, captures an agent's attempt to include jokes in its dialog. Several studies in our reviewed corpus have explored the effect of humour on various perceptions of agents (e.g. \cite{ceha2021can}\cmt{[57]}\cite{khooshabeh2011does}\cmt{[37]}).

The category of \textbf{content style} refers to the variations of language used in a message aside from the content meaning of the message (i.e. how something is said). The element of \textit{formality} describes the linguistic style used by the conversational agent, whether it is formal vs. casual, such as using honorific expressions to address users \cite{ouchi2019should}\cmt{[59]}. \textit{Alignment} captures the degree that the agent aligns its utterances to the users, such as lexical alignment on the content and structural of the sentences \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, as well as referring and agreeing with users' utterances \cite{volkel2021examining}\cmt{[69]}. Lastly, the element of \textit{elaborateness} captures the sentence complexity and length of agents' utterances. For example, Roy et al. explored the differences in perception for variations in elaborateness such as "Cloudly, possibility of snow, high: 4, low: -10" vs "Today will be cloudy, with a high of 4 and a low of -10. Snow is predicted" \cite{roy2021users}\cmt{[71]}.

Lastly, the category of \textbf{speech format} captures the non-verbal component of a conversational agent's utterances for both text and voice modalities. \textit{Disfluency} captures 
the use of non-lexical utterances like filler words ("um, uh") \cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}, or repetition of words within a sentence \cite{yang2021effect}\cmt{[72]}. It also includes the format of using typos \cite{westerman2019believe}\cmt{[9]} for text-based agents. For voice-based agents specifically, the element of \textit{prosody} encompasses vocal qualities like pitch \cite{habler2019effects}\cmt{[63]}\cite{jestin2022effects}\cmt{[81]}, speech rate \cite{choi2020nobody}\cmt{[54]}, and spoken accent \cite{feijoo2021effects}\cmt{[70]}. For text-based CAs, the \textit{text formatting} element includes different formats agents uses to present information to users, such as using capitalization \cite{westerman2019believe}\cmt{[9]} or emoticons \cite{kim2019comparing}\cmt{[89]}\cite{wilhelm2022keep}\cmt{[28]}.

Overall there are similar number of conversation architecture elements explored across the four categories of dialog strategy, content affectiveness, content style, and speech format. As for explorations related to different modalities of agents, there is a noticeable difference in the category of speech format, where architecture elements related to voice-based agents (n=15) are explored more than text-based agents (n=7). Looking across the 12 different elements, there is good coverage of studies on the impact of affective language and prosody cues on the perceptions of agents. However, there are less studies exploring the effect of agent initiated content and response delay on the perception of agents. Specifically for the element of initiative under dialog strategy category, there is literature on conversation repairs \cite{komatani2010online}\cite{reinkemeier2022repair} and agent proactively sharing content with users \cite{dubiel2019inquisitive}\cite{zargham2022understanding}, but many of them did not not include assessments of perceptions of the CA. This may be due to the fact that the usage of agent-initiated content is relatively new, as CA interactions have historically been driven by users. As such, current research is focused on the functional aspects of agents initiating contents instead of exploring the perceptions of agents. As for response delay, there are indications that this element is under-explored in literature. Only 4 studies in our reviewed corpus used an agent with response delay, and the majority of these publications were written by the same authors.

@@

There are 183 identified relationships between perceptions of agents and conversation architecture out of the 265 explored connections that are included in our synthesized framework (Figure \ref{fig:heatmap_identified}). To compare the number of identified relationships vs. the explored connections in literature, Figure \ref{fig:heatmap_coverage} shows a side-by-side comparison between the two. The detailed analysis on the differences between explored and identified relationships are discussed in the subsections below.

@@

Across the aspects for the perception of interaction, both usability and engagement were assessed frequently in the reviewed literature, with conversation architecture having effects on these perception aspects across all architecture element categories. The aspect of satisfaction was used in some studies to evaluate perception but it is not used as often as engagement or usability. Several papers that assessed user satisfactions were conversation agents within the transaction context, especially within the customer service domain (e.g. \cite{diederich2019emulating}\cmt{[25]}\cite{elsholz2019exploring}\cmt{[61]}\cite{gnewuch2018faster}\cmt{[19]}).

The category of conversation architecture elements with the most identified relationships to perceptions of interaction is content style. Specifically for the element of \textit{elaborateness}, users found the use of full sentences more useful than keyword only \cite{haas2022keep}\cmt{[78]}\cite{roy2021users}\cmt{[71]}. Otherwise, the effect of an agent's elaborateness on user's perception of interaction depends on the user's preference \cite{miehle2018exploring}\cmt{[51]}, as well as the topic of discussion \cite{haas2022keep}\cmt{[78]}. As for \textit{formality}, various studies reported significant differences in perceptions of interaction between using casual vs. formal styles. Some users experienced higher engagement with agent interacting with the casual style of the conversation \cite{cox2022does}\cmt{[27]}, while in another study users reported the formal language style as less engaging as it is boring \cite{kim2019comparing}\cmt{[89]}.

The speech format of an agent also resulted in a high number of identified relationships with the perception of interaction with CAs, with majority of the explored connections resulted in effects between the perception aspects and architecture elements. The element with the most identified relationships is \textit{prosody}. For example, studies found that a CA's expressiveness in vocal cues increased participants' engagement ratings \cite{zhu2022effects}\cmt{[26]}, and different pitches of voice affect users' perception of engagement and usability \cite{chan2021kinvoices}\cmt{[74]}\cite{habler2019effects}\cmt{[63]}.

Dialog strategy and content affectiveness categories of conversation architecture did not have as many identified relationships with perceptions of interaction. It is worth noting the effect of using the \textit{initiative} element, as CAs that use self-initiated content are perceived as more efficient and higher quality of interaction (e.g. \cite{cuadra2021my}\cmt{[67]}). Also, some studies have discovered conflicting effects between different perception aspects of interaction for CAs using \textit{social dialog}, as users enjoyed the conversation using social talk \cite{lee2020hear}\cmt{[23]}\cite{roy2021users}\cmt{[71]}, but perceived the CA as less efficient \cite{roy2021users}\cmt{[71]}.

@@

Out of the explored conversation architecture elements, \textit{prosody} had relationships identified with aspects across the perception category of agent's ability. For example, Chan et al. \cite{chan2021kinvoices}\cmt{[74]} found that agents using kin's voices are rated as more intelligent and credible than generic voices. Also, the style of speech used by an agent affects the perception of appropriateness of tone, which is an aspect of the perceived competence of an agent \cite{misu2011toward}\cmt{[83]}. Different content styles of \textit{formality} also impacts the perceived competence of an agent \cite{cox2022does}\cmt{[27]}\cite{jestin2022effects}\cmt{[81]}. Specifically related to perceived credibility of an agent, being \textit{lexically aligned} with the user resulted improved the rating of trustworthiness of an agent \cite{hoegen2019end}\cmt{[31]}\cite{linnemann2018can}\cmt{[15]}. There were mixed results on the use of emoticons within the \textit{text formatting} element. One study found the chatbot using emoticons as less trustworthy \cite{wilhelm2022keep}\cmt{[28]}, while another study found that users assigned higher scores for confidence to the agent using emojis \cite{fadhil2018effect}\cmt{[52]}.

@@

The perception of agent's humanness is the second most explored category within our reviewed corpus (n=64), with majority of the connections identified relationship between the studied conversation architecture elements and the anthropomorphized perceptions of agent (n=49). Interestingly, studies explored more perceptions of sociability with agent related to voice-based CAs (n=40) compared to text-based CAs (n=24), potentially due to the assumption that interactions with text-based agents are perceived as less personal and more formal \cite{kocielnik2018designing}. There are some mixed results for voice-based CAs, as 12 out of the 28 connections did not find any significant results. Drilling down to the specific elements, we noticed that the use of \textit{alignment} in voice-based agents did not effect the perception of sociability with agent \cite{healey2013relating}\cmt{[39]}\cite{linnemann2018can}\cmt{[15]}. We didn't have data on text-based agents' perceived social connections with users to compare with voice-based agents, as the studies using alignment and text modality in our corpus did not assess this aspect category of perception.

@@

Looking at the different categories of conversation architecture elements, the heatmap (Figure \ref{fig:heatmap-impact} shows that there are not many relationships in content style category that are related to the perceived sociability with CAs in general, with most of the discovered effects concentrated at the intersection of \textit{formality} and conversation tone. Studies have found that CAs using casual style of conversation are perceived as warm, empathetic and friendly \cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}, while CAs using formal style of conversation are perceived as polite but lacks empathy \cite{cox2022does}\cmt{[27]}. The rest of the architecture elements and perception aspects of sociability are minimally explored in literature, which indicates the need for more research in this area.

There are a few specific conversation architecture elements that had more identified relationships with perceptions of sociability with agent. Specifically, CAs using of \textit{affective language} were perceived to be more empathetic \cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{yang2017perceived}\cmt{[44]} and emotionally expressive \cite{zhu2022effects}\cmt{[26]}, as well as being more emotional connected with their users \cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}. Also, different variations of a voice-based CA's \textit{prosody} have effects on the perceived sociability with agent, such as an agent using expressive prosody is assessed as more intimate and more similar with the user \cite{kim2020can}\cmt{[24]}. Lastly, the conversation architecture element of \textit{humour} has identified relationships across the social connection category of perception. Clark et al. \cite{clark2019makes} found that humour is an important conversational characteristic for human-human interactions, but viewed as a novelty feature for human-agent conversations. However, in our review we found that humor has effects on human-agent relationships, as humorous agents are rated as more friendly, intimate, and similar by users compared to non-humorous agents \cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}.

@@

There are a few notable conversation architecture elements related to the perceived humanness of conversational agents. The use of \textit{prosody} such as varying pitch, intonation and speech rate has more identified relationships with the perceived personality traits of an agent as compared to the perceived human-likeness, especially on the aspect of likeability \cite{choi2020nobody}\cmt{[54]}\cite{jestin2022effects}\cmt{[81]}\cite{misu2011toward}\cmt{[83]}. For the architecture elements of \textit{disfluency}, the type of impact on the perception of humanness depended on the context of the conversation. Studies have found that participants perceived the filler-condition agent as more likeable in the social-oriented situation, but did not find the same effect in task-oriented situations \cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}. The use of \textit{alignment} in an agent had a number of identified relationships with the perception of personality traits, with some studies finding CAs that are lexically aligned with a user are more likeable \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}.

>>>>

The category of \textbf{dialog strategy} refers to the approach used by a conversational agent to engage in a dialogue with a user, which includes the use of social dialogs, agent-initiated content, and adding delays to responses. Specifically, the element of \textit{social dialogue} captures non-task related conversations with the user to build social connection, such as self-disclosure \cite{lee2020hear}\cmt{[23]} and small talk like chitchats \cite{lubold2016effects, volkel2021manipulating}\cmt{[86][68]}. The element of \textit{initiative} captures utterances that are initiated by the agent without direct prompts from the user. For example, the agent is taking the initiative to proactively repair the conversation with a user \cite{ashktorab2019resilient, cuadra2021my}\cmt{[88][67]}, or actively elicit feedback from users \cite{xiao2021let}\cmt{[73]}. Lastly, \textit{response delay} refers to the tactic of deliberately delaying for a certain period of time before an agent responds to users \cite{gnewuch2018faster, gnewuch2022opposing}\cmt{[19][20]}. It is mainly used in text-based CAs alongside visual displays of typing indicators \cite{gnewuch2018chatbot}\cmt{[21]}.

\textbf{Content affectiveness} refers to the conversational agent's use of language to convey emotions or to elicit emotions from users. The architecture element of \textit{affective language} captures the injection of emotional words or phrases into the agent's utterance, such as affective expressions \cite{seeger2021chatbots, yang2017perceived, zhu2022effects}\cmt{[35][44][26]}, sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, and encouraging words \cite{healey2013relating}\cmt{[39]}. The other element in this category, \textit{humour}, captures an agent's attempt to include jokes in its dialog. Several studies in our reviewed corpus have explored the effect of humour on various perceptions of agents (e.g. \cite{ceha2021can, khooshabeh2011does}\cmt{[57][37]}).

The category of \textbf{content style} refers to the variations of language used in a message aside from the content meaning of the message (i.e. how something is said). The element of \textit{formality} describes the linguistic style used by the conversational agent, whether it is formal vs. casual, such as using honorific expressions to address users \cite{ouchi2019should}\cmt{[59]}. \textit{Alignment} captures the degree that the agent aligns its utterances to the users, such as lexical alignment on the content and structural of the sentences \cite{huiyang2022improving, linnemann2018can}\cmt{[17][15]}, as well as referring and agreeing with users' utterances \cite{volkel2021examining}\cmt{[69]}. Lastly, the element of \textit{elaborateness} captures the sentence complexity and length of agents' utterances. For example, Roy et al. explored the differences in perception for variations in elaborateness such as "Cloudly, possibility of snow, high: 4, low: -10" vs "Today will be cloudy, with a high of 4 and a low of -10. Snow is predicted" \cite{roy2021users}\cmt{[71]}.

Lastly, the category of \textbf{speech format} captures the non-verbal component of a conversational agent's utterances for both text and voice modalities. \textit{Disfluency} captures 
the use of non-lexical utterances like filler words ("um, uh") \cite{hu2021enhancing, jeong2019exploring}\cmt{[56][10]}, or repetition of words within a sentence \cite{yang2021effect}\cmt{[72]}. It also includes the format of using typos \cite{westerman2019believe}\cmt{[9]} for text-based agents. For voice-based agents specifically, the element of \textit{prosody} encompasses vocal qualities like pitch \cite{habler2019effects, jestin2022effects}\cmt{[63][81]}, speech rate \cite{choi2020nobody}\cmt{[54]}, and spoken accent \cite{feijoo2021effects}\cmt{[70]}. For text-based CAs, the \textit{text formatting} element includes different formats agents uses to present information to users, such as using capitalization \cite{westerman2019believe}\cmt{[9]} or emoticons \cite{kim2019comparing, wilhelm2022keep}\cmt{[89][28]}.

Overall there are similar number of conversation architecture elements explored across the four categories of dialog strategy, content affectiveness, content style, and speech format. As for explorations related to different modalities of agents, there is a noticeable difference in the category of speech format, where architecture elements related to voice-based agents (n=15) are explored more than text-based agents (n=7). Looking across the 12 different elements, there is good coverage of studies on the impact of affective language and prosody cues on the perceptions of agents. However, there are less studies exploring the effect of agent initiated content and response delay on the perception of agents. Specifically for the element of initiative under dialog strategy category, there is literature on conversation repairs \cite{komatani2010online, reinkemeier2022repair} and agent proactively sharing content with users \cite{dubiel2019inquisitive, zargham2022understanding}, but many of them did not not include assessments of perceptions of the CA. This may be due to the fact that the usage of agent-initiated content is relatively new, as CA interactions have historically been driven by users. As such, current research is focused on the functional aspects of agents initiating contents instead of exploring the perceptions of agents. As for response delay, there are indications that this element is under-explored in literature. Only 4 studies in our reviewed corpus used an agent with response delay, and the majority of these publications were written by the same authors.

@@

There are 183 identified relationships between perceptions of agents and conversation architecture out of the 265 explored connections that are included in our synthesized framework (\autoref{fig:heatmap_identified}). To compare the number of identified relationships vs. the explored connections in literature, \autoref{fig:heatmap_coverage} shows a side-by-side comparison between the two. The detailed analysis on the differences between explored and identified relationships are discussed in the subsections below.

@@

Across the aspects for the perception of interaction, both usability and engagement were assessed frequently in the reviewed literature, with conversation architecture having effects on these perception aspects across all architecture element categories. The aspect of satisfaction was used in some studies to evaluate perception but it is not used as often as engagement or usability. Several papers that assessed user satisfactions were conversation agents within the transaction context, especially within the customer service domain (e.g. \cite{diederich2019emulating, elsholz2019exploring, gnewuch2018faster}\cmt{[25][61][19]}).

The category of conversation architecture elements with the most identified relationships to perceptions of interaction is content style. Specifically for the element of \textit{elaborateness}, users found the use of full sentences more useful than keyword only \cite{haas2022keep, roy2021users}\cmt{[78][71]}. Otherwise, the effect of an agent's elaborateness on user's perception of interaction depends on the user's preference \cite{miehle2018exploring}\cmt{[51]}, as well as the topic of discussion \cite{haas2022keep}\cmt{[78]}. As for \textit{formality}, various studies reported significant differences in perceptions of interaction between using casual vs. formal styles. Some users experienced higher engagement with agent interacting with the casual style of the conversation \cite{cox2022does}\cmt{[27]}, while in another study users reported the formal language style as less engaging as it is boring \cite{kim2019comparing}\cmt{[89]}.

The speech format of an agent also resulted in a high number of identified relationships with the perception of interaction with CAs, with majority of the explored connections resulted in effects between the perception aspects and architecture elements. The element with the most identified relationships is \textit{prosody}. For example, studies found that a CA's expressiveness in vocal cues increased participants' engagement ratings \cite{zhu2022effects}\cmt{[26]}, and different pitches of voice affect users' perception of engagement and usability \cite{chan2021kinvoices, habler2019effects}\cmt{[74][63]}.

Dialog strategy and content affectiveness categories of conversation architecture did not have as many identified relationships with perceptions of interaction. It is worth noting the effect of using the \textit{initiative} element, as CAs that use self-initiated content are perceived as more efficient and higher quality of interaction (e.g. \cite{cuadra2021my}\cmt{[67]}). Also, some studies have discovered conflicting effects between different perception aspects of interaction for CAs using \textit{social dialog}, as users enjoyed the conversation using social talk \cite{lee2020hear, roy2021users}\cmt{[23][71]}, but perceived the CA as less efficient \cite{roy2021users}\cmt{[71]}.

@@

Out of the explored conversation architecture elements, \textit{prosody} had relationships identified with aspects across the perception category of agent's ability. For example, Chan et al. \cite{chan2021kinvoices}\cmt{[74]} found that agents using kin's voices are rated as more intelligent and credible than generic voices. Also, the style of speech used by an agent affects the perception of appropriateness of tone, which is an aspect of the perceived competence of an agent \cite{misu2011toward}\cmt{[83]}. Different content styles of \textit{formality} also impacts the perceived competence of an agent \cite{cox2022does, jestin2022effects}\cmt{[27][81]}. Specifically related to perceived credibility of an agent, being \textit{lexically aligned} with the user resulted improved the rating of trustworthiness of an agent \cite{hoegen2019end, linnemann2018can}\cmt{[31][15]}. There were mixed results on the use of emoticons within the \textit{text formatting} element. One study found the chatbot using emoticons as less trustworthy \cite{wilhelm2022keep}\cmt{[28]}, while another study found that users assigned higher scores for confidence to the agent using emojis \cite{fadhil2018effect}\cmt{[52]}.

@@

The perception of agent's humanness is the second most explored category within our reviewed corpus (n=64), with majority of the connections identified relationship between the studied conversation architecture elements and the anthropomorphized perceptions of agent (n=49). Interestingly, studies explored more perceptions of sociability with agent related to voice-based CAs (n=40) compared to text-based CAs (n=24), potentially due to the assumption that interactions with text-based agents are perceived as less personal and more formal \cite{kocielnik2018designing}. There are some mixed results for voice-based CAs, as 12 out of the 28 connections did not find any significant results. Drilling down to the specific elements, we noticed that the use of \textit{alignment} in voice-based agents did not effect the perception of sociability with agent \cite{healey2013relating, linnemann2018can}\cmt{[39][15]}. We didn't have data on text-based agents' perceived social connections with users to compare with voice-based agents, as the studies using alignment and text modality in our corpus did not assess this aspect category of perception.

@@

Looking at the different categories of conversation architecture elements, the heatmap (\autoref{fig:heatmap_identified}) shows that there are not many relationships in content style category that are related to the perceived sociability with CAs in general, with most of the discovered effects concentrated at the intersection of \textit{formality} and conversation tone. Studies have found that CAs using casual style of conversation are perceived as warm, empathetic and friendly \cite{jestin2022effects, kim2019comparing}\cmt{[81][89]}, while CAs using formal style of conversation are perceived as polite but lacks empathy \cite{cox2022does}\cmt{[27]}. The rest of the architecture elements and perception aspects of sociability are minimally explored in literature, which indicates the need for more research in this area.

There are a few specific conversation architecture elements that had more identified relationships with perceptions of sociability with agent. Specifically, CAs using of \textit{affective language} were perceived to be more empathetic \cite{daher2020empathic, diederich2019emulating, yang2017perceived}\cmt{[58][25][44]} and emotionally expressive \cite{zhu2022effects}\cmt{[26]}, as well as being more emotional connected with their users \cite{lee2019s, lubis2019positive}\cmt{[55][43]}. Also, different variations of a voice-based CA's \textit{prosody} have effects on the perceived sociability with agent, such as an agent using expressive prosody is assessed as more intimate and more similar with the user \cite{kim2020can}\cmt{[24]}. Lastly, the conversation architecture element of \textit{humour} has identified relationships across the social connection category of perception. Clark et al. \cite{clark2019makes} found that humour is an important conversational characteristic for human-human interactions, but viewed as a novelty feature for human-agent conversations. However, in our review we found that humor has effects on human-agent relationships, as humorous agents are rated as more friendly, intimate, and similar by users compared to non-humorous agents \cite{go2021conversational, khooshabeh2011does}\cmt{[80][37]}.

@@

There are a few notable conversation architecture elements related to the perceived humanness of conversational agents. The use of \textit{prosody} such as varying pitch, intonation and speech rate has more identified relationships with the perceived personality traits of an agent as compared to the perceived human-likeness, especially on the aspect of likeability \cite{choi2020nobody, jestin2022effects, misu2011toward}\cmt{[54][81][83]}. For the architecture elements of \textit{disfluency}, the type of impact on the perception of humanness depended on the context of the conversation. Studies have found that participants perceived the filler-condition agent as more likeable in the social-oriented situation, but did not find the same effect in task-oriented situations \cite{jeong2019exploring, wester2015artificial}\cmt{[10][14]}. The use of \textit{alignment} in an agent had a number of identified relationships with the perception of personality traits, with some studies finding CAs that are lexically aligned with a user are more likeable \cite{huiyang2022improving, linnemann2018can}\cmt{[17][15]}.

### 2023-02-22 sections/5-discussion.tex
Young-Ho edit and fix citations/references

As we gain a better understanding about the effects of a single conversation architecture element on the perceptions of agents, we can extend the research to using \textit{multiple conversation architecture elements} in an agent. Several papers in our reviewed corpus incorporated composite elements in an agent, such as the design of an anthropomorphized chatbot using elements such as affective language, emoticons, response delays to assess users' perceptions compared to a non-anthropomorphized chatbot \cite{seeger2021chatbots}\cmt{[35]}. In addition to explore the combined effects of conversation architecture elements on users' perceptions, it would also be interesting to understand the relative importance of each element on perceptions. Some studies analyzed the effect of modifying conversation architecture elements individually, as well as their combined effect on user's perceptions (e.g. \cite{habler2019effects}\cmt{[63]}\cite{lubold2016effects}\cmt{[86]}\cite{zhu2022effects}\cmt{[26]}). Specifically, Habler et al. \cite{habler2019effects}\cmt{[63]} found that the effect for social dialog is higher than the effect for prosody on the perception of agents.

@@

For the element of prosody, various studies in our corpus explored the effect of different pitches on the perceptions of agents. Even in studies that are not explicitly analyzing the effect of different gendered voices in an agent, possible stereotypes may still exist in the study. Based on our reviewed corpus, studies found that lower pitches commonly associated with men are considered to be more desirable, authoritative but less friendly \cite{tolmeijer2021female}\cmt{[62]}\cite{jestin2022effects}\cmt{[81]}. For Dubiel et al's study \cite{dubiel2020persuasive}\cmt{[60]}, the agent with lower mean pitch was selected as the more persuasive voice. These results may be demonstrating users' unconscious bias to select a male sounding voice as more persuasive and authoritative over female sounding voices that are commonly associated with higher pitches. While some guidelines recommend designing agents to be androgynous to avoid gender stereotypes \cite{ruane2019conversational}, there are limitations in creating gender-ambiguous voices. Currently there is no defined guidelines on what is perceived as a gender-neutral voice \cite{jestin2022effects}\cmt{[81]}. There is also a lack of voice generators available to generate voices that are perceived as androgynous \cite{tolmeijer2021female}\cmt{[62]}.

@@

Another key area of concern is privacy. Given the natural language format of conversational agents, users may be disclosing more sensitive and personal information than needed for the interaction. In relationship to conversation architecture, using elements like self-disclosure and persuasive voice prosody settings could result in users perceiving higher trust with the agent, leading them to disclose more sensitive information  \cite{lee2020hear}\cmt{[23]}\cite{dubiel2020persuasive}\cmt{[60]}. This can expose users to attacks, such as CAs using voice impersonation to ask for personal information for malicious intents \cite{chan2021kinvoices}\cmt{[74]}. Designing for perceptions of agents requires careful consideration of privacy issues including the sensitivity of the data, who has access to it, and how to protect against nefarious users.

>>>>

As we gain a better understanding about the effects of a single conversation architecture element on the perceptions of agents, we can extend the research to using \textit{multiple conversation architecture elements} in an agent. Several papers in our reviewed corpus incorporated composite elements in an agent, such as the design of an anthropomorphized chatbot using elements such as affective language, emoticons, response delays to assess users' perceptions compared to a non-anthropomorphized chatbot \cite{seeger2021chatbots}\cmt{[35]}. In addition to explore the combined effects of conversation architecture elements on users' perceptions, it would also be interesting to understand the relative importance of each element on perceptions. Some studies analyzed the effect of modifying conversation architecture elements individually, as well as their combined effect on user's perceptions (e.g. \cite{habler2019effects, lubold2016effects, zhu2022effects}\cmt{[63][86][26]}). Specifically, Habler et al. \cite{habler2019effects}\cmt{[63]} found that the effect for social dialog is higher than the effect for prosody on the perception of agents.

@@

For the element of prosody, various studies in our corpus explored the effect of different pitches on the perceptions of agents. Even in studies that are not explicitly analyzing the effect of different gendered voices in an agent, possible stereotypes may still exist in the study. Based on our reviewed corpus, studies found that lower pitches commonly associated with men are considered to be more desirable, authoritative but less friendly \cite{jestin2022effects, tolmeijer2021female}\cmt{[81][62]}. For Dubiel et al's study \cite{dubiel2020persuasive}\cmt{[60]}, the agent with lower mean pitch was selected as the more persuasive voice. These results may be demonstrating users' unconscious bias to select a male sounding voice as more persuasive and authoritative over female sounding voices that are commonly associated with higher pitches. While some guidelines recommend designing agents to be androgynous to avoid gender stereotypes \cite{ruane2019conversational}, there are limitations in creating gender-ambiguous voices. Currently there is no defined guidelines on what is perceived as a gender-neutral voice \cite{jestin2022effects}\cmt{[81]}. There is also a lack of voice generators available to generate voices that are perceived as androgynous \cite{tolmeijer2021female}\cmt{[62]}.

@@

Another key area of concern is privacy. Given the natural language format of conversational agents, users may be disclosing more sensitive and personal information than needed for the interaction. In relationship to conversation architecture, using elements like self-disclosure and persuasive voice prosody settings could result in users perceiving higher trust with the agent, leading them to disclose more sensitive information  \cite{dubiel2020persuasive, lee2020hear}\cmt{[60][23]}. This can expose users to attacks, such as CAs using voice impersonation to ask for personal information for malicious intents \cite{chan2021kinvoices}\cmt{[74]}. Designing for perceptions of agents requires careful consideration of privacy issues including the sensitivity of the data, who has access to it, and how to protect against nefarious users.
